candidate genes

### 2019-10-12 analysis/10_specificgenes.Rmd
remove head

---
title: "forvictoria"
output: md_document
---

@@

row.names(hypcounts) <- hypcounts$Name
hypcounts$Name <- NULL
hypcounts$entrezid <- NULL
hypcandidatecounts <- as.data.frame(t(hypcounts))
hypcandidatecounts$V1 <- row.names(hypcandidatecounts)
hypcandidatecounts <- left_join(hypsamples, hypcandidatecounts)
head(hypcandidatecounts)

>>>>

---
title: "candidate genes"
output: md_document
---

@@

row.names(hypcounts) <- hypcounts$Name
hypcounts$Name <- NULL
hypcounts$entrezid <- NULL
hypcandidatecounts <- as.data.frame(t(hypcounts))
hypcandidatecounts$V1 <- row.names(hypcandidatecounts)
hypcandidatecounts <- left_join(hypsamples, hypcandidatecounts)
